---
title: >
  Radcliffe Camera
author:
- name: Kevin Rue-Albrecht
  affiliation: 
  - &id4 MRC WIMM Centre for Computational Biology, University of Oxford, Oxford, OX3 9DS, UK
  email: kevinrue67@gmail.com
date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('spatialist')`"
output: 
  BiocStyle::html_document:
    toc: true
    toc_depth: 2
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Radcliffe Camera}
  %\VignetteEncoding{UTF-8}  
  %\VignettePackage{spatialist}
  %\VignetteKeywords{Visualization}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
bibliography: spatialist.bib
---

**Compiled date**: `r Sys.Date()`

**Last edited**: 2020-04-20

**License**: `r packageDescription("spatialist")[["License"]]`

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    error = FALSE,
    warning = FALSE,
    message = FALSE,
    crop = NULL
)
stopifnot(requireNamespace("htmltools"))
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

# Introduction 

`r BiocStyle::Githubpkg("kevinrue/spatialist")` is an *R* package.

Once installed, the package can be loaded and attached to your current workspace as follows:

```{r library, message=FALSE}
library(spatialist)
```

Other helpful libraries.

```{r, message=FALSE}
library(ggplot2)
```

# Demonstration

## Input file

```{r}
input_file <- tempfile(fileext = ".jpg")
dir.create(dirname(input_file))
download.file(url = "https://lh3.googleusercontent.com/p/AF1QipOCPWTCh3keAMBioweiqUf0PZHOaxIUCekJThB9=s1360-w1360-h1020", destfile = input_file)
```

## Output types

### Raw image

```{r raw}
spatial_thing <- spatialise(
  path = input_file
)
print(spatial_thing)
```

### Flattened image

```{r flatten}
spatial_thing <- spatialise(
  path = input_file,
  return.type = "flatten",
  extras = list(
    image_flatten = list(operator = "Modulate")
  )
)
print(spatial_thing)
```

### Image data

```{r data}
spatial_thing <- spatialise(
  path = input_file,
  return.type = "data"
)
spatial_thing
```

### Processed matrix

```{r matrix}
spatial_thing <- spatialise(
  path = input_file,
  return.type = "matrix"
)
dim(spatial_thing)
```

### Heat map (of matrix)

```{r heatmap, fig.height=6, fig.width=7}
spatialise(
  path = input_file,
  return.type = "heatmap"
)
```

### Pixel coordinates

```{r xy, fig.height=6, fig.width=7}
spatial_thing <- spatialise(
  path = input_file,
  return.type = "xy"
)
head(spatial_thing)
```

### Scatter plot

```{r point, fig.height=6, fig.width=7}
spatialise(
  path = input_file,
  return.type = "point",
  downsample = 100
) + theme_void()
```

### Jittered scatter plot

```{r jitter, fig.height=6, fig.width=7}
spatialise(
  path = input_file,
  return.type = "jitter",
  downsample = 100,
  jitter = 5
) + theme_void()
```

### Xenium-like

```{r spatial, fig.height=6, fig.width=7}
spatialise(
  path = input_file,
  return.type = "spatial",
  downsample = 150,
  jitter = 3,
  point.size = 0.5,
  extras = list(
    cluster = list(k.nn = 50, k.cluster = 9)
  )
) + 
  coord_cartesian(ylim = c(NA, -90)) +
  theme_void() + guides(colour = "none") +
  scale_colour_brewer(palette = "Paired")
```

### Visium-like

```{r visium, fig.height=6, fig.width=7}
spatialise(
  path = input_file,
  return.type = "visium",
  downsample = 200,
  point.size = 0.1,
  extras = list(
    cluster = list(k.nn = 50, k.cluster = 10)
  )
) + 
  coord_cartesian(ylim = c(NA, -90)) +
  theme_void() + guides(colour = "none") +
  scale_colour_brewer(palette = "Paired")
```

# Additional information

The GitHub repository contains the development version of the package, where new functionality is added over time.
The authors appreciate well-considered suggestions for improvements or new features, or even better, pull requests.

If you use `r BiocStyle::Githubpkg("kevinrue/spatialist")` for your analysis, please cite it as shown below:

```{r citation}
citation("spatialist")
```

# Session Info {.unnumbered}

```{r sessioninfo}
sessionInfo()
```

# References {.unnumbered}
