---
title: >
  Spotify Yourself
author:
- name: Kevin Rue-Albrecht
  affiliation: 
  - &id1 MRC WIMM Centre for Computational Biology, University of Oxford, Oxford, OX3 9DS, UK
  email: kevinrue67@gmail.com
date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('spotify')`"
output: 
  BiocStyle::html_document:
    toc: true
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Spotify Yourself}
  %\VignetteEncoding{UTF-8}  
  %\VignettePackage{spotify}
  %\VignetteKeywords{Visualization}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
bibliography: spotify.bib
---

**Compiled date**: `r Sys.Date()`

**Last edited**: 2020-04-20

**License**: `r packageDescription("spotify")[["License"]]`

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    error = FALSE,
    warning = FALSE,
    message = FALSE,
    crop = NULL
)
stopifnot(requireNamespace("htmltools"))
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

# Introduction 

`r BiocStyle::Githubpkg("kevinrue/spotify")` is an *R* package.

Once installed, the package can be loaded and attached to your current workspace as follows:

```{r library, message=FALSE}
library(spotify)
```

Other helpful libraries.

```{r, message=FALSE}
library(ggplot2)
```

# Demonstration

## Input file

```{r}
input_file <- system.file(package = "spotify", "spotify.jpg")
```

## Output types

### Raw image

```{r raw, fig.alt = "Raw image."}
kevin <- spotify(
  path = input_file
)
print(kevin)
```

### Flattened image

```{r flatten, fig.alt = "Flattened image."}
kevin <- spotify(
  path = input_file,
  return.type = "flatten",
  extras = list(
    image_flatten = list(operator = "Modulate")
  )
)
print(kevin)
```

### Image data

```{r data}
kevin <- spotify(
  path = input_file,
  return.type = "data"
)
kevin
```

### Processed matrix

```{r matrix}
kevin <- spotify(
  path = input_file,
  return.type = "matrix",
  invert = TRUE
)
dim(kevin)
```

### Heat map

```{r heatmap, fig.alt = "Heat map.", fig.height=6, fig.width=7}
spotify(
  path = input_file,
  return.type = "heatmap",
  invert = TRUE
)
```

### Pixel coordinates

```{r xy}
kevin <- spotify(
  path = input_file,
  return.type = "xy",
  invert = TRUE
)
head(kevin)
```

### Scatter plot

```{r point, fig.alt = "Scatter plot."}
spotify(
  path = input_file,
  return.type = "point",
  invert = TRUE,
  downsample = 100
) + theme_void()
```

### Jittered scatter plot

```{r jitter, fig.alt = "Jittered scatter plot."}
spotify(
  path = input_file,
  return.type = "jitter",
  invert = TRUE,
  downsample = 100,
  jitter = 5
) + theme_void()
```

### Xenium-like

```{r spatial, fig.alt = "Xenium-like plot."}
spotify(
  path = input_file,
  return.type = "spatial",
  invert = TRUE,
  downsample = 75,
  jitter = 5,
  extras = list(
    cluster = list(k.nn = 50, k.cluster = 10)
  )
) + theme_void() + guides(colour = "none")
```

### Visium-like

```{r visium, fig.alt = "Visium-like plot."}
spotify(
  path = input_file,
  return.type = "visium",
  invert = TRUE,
  downsample = 100,
  point.size = 0.25,
  extras = list(
    cluster = list(k.nn = 50, k.cluster = 10)
  )
) + theme_void() + guides(colour = "none")
```

# Additional information

The GitHub repository contains the development version of the package, where new functionality is added over time.
The authors appreciate well-considered suggestions for improvements or new features, or even better, pull requests.

If you use `r BiocStyle::Githubpkg("kevinrue/spotify")` for your analysis, please cite it as shown below:

```{r citation}
citation("spotify")
```

# Session Info {.unnumbered}

```{r sessioninfo}
sessionInfo()
```

# References {.unnumbered}
